---
title: "TwitterTextAnalysis"
author: "SaiPuneeth Chinnam"
date: "15/12/2021"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. Computed word frequencies for each year. Exclude the stop words
```{r}
library(dplyr)
library(stringr)
library(tidytext)
library(janeaustenr)
library(ggplot2)
library(tidyr)
library(igraph)
library(ggraph)
library(stopwords)

elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))



elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only


wordscount <-elon%>%
unnest_tokens(word,tweet) %>%
 count(date, word, sort=TRUE)
  
wordscount <- wordscount%>%
  filter(date >2016)

new_df = wordscount%>%
filter(!(word %in% stopwords("en", source = "snowball")))


Extrastopwords = c('just','yes','next','like','dont','make', 'get','ppathhole','much','also','can','soon','year')
new_df = new_df%>%
  filter(!(word %in% Extrastopwords))

totalcount <- new_df %>% 
  group_by(date) %>% 
  summarize(total = sum(n))      #Calculating total words for respective year

wordscount <- left_join(new_df,totalcount)

# wordscount%>%
#   filter(date > 2016)
  



freqbyrank <- wordscount %>% 
  group_by(date) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total) %>%
  ungroup()

freqbyrank

```

#2. Showing top 10 words (for each year) by the highest value of word frequency
```{r}
df17= freqbyrank%>%
  filter(date == 2017)%>%
  head(10)
  
df17


df18= freqbyrank%>%
  filter(date == 2018)%>%
  head(10)
df18

  
df19= freqbyrank%>%
  filter(date == 2019)%>%
  head(10)
df19


df20= freqbyrank%>%
  filter(date == 2020)%>%
  head(10)
df20


df21= freqbyrank%>%
  filter(date == 2021)%>%
  head(10)
df21
```

#3. Plotting histogram of word frequencies for each year
```{r}
#Histogram for word frequencies for each year

ggplot(wordscount, aes(n/total, fill = date)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~date, ncol = 3, scales = "free_y")
```

#4. Using Zipf’s law and plotting log-log plots of word frequencies and rank for each year
```{r}
#Zipf's Law

freqbyrank <- wordscount %>% 
  group_by(date) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total) %>%
  ungroup()

freqbyrank %>% 
  ggplot(aes(rank, `term frequency`, color = date)) + 
  geom_line(size = .5, alpha = 1, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()

lm(log10(`term frequency`) ~ log10(rank), data = freqbyrank) #To get intercept and slope


 
freqbyrank %>% 
  ggplot(aes(rank, `term frequency`, color = date)) + 
  geom_abline(intercept = -0.9107, slope = -0.9753, #To plot with respect to line
              color = "gray5", linetype = 2) +
  geom_line(size = .5, alpha = 1, show.legend = TRUE) + 
  scale_x_log10() +
  scale_y_log10()

```

#5. Creating bigram network graphs for each year


#Bigrams for year 2017
```{r}
library(dplyr)
library(stringr)
library(tidytext)
library(janeaustenr)
library(ggplot2)
library(tidyr)
library(igraph)
library(ggraph)
library(stopwords)
elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))

elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only

elon <- elon%>%
  filter(date == 2017)

elonbigrams <- elon %>%
  unnest_tokens(bigram, tweet, token = "ngrams", n = 2)

elonbigrams %>%
  count(bigram, sort = TRUE)

# bigrams with stop words
bigramsseparated <- elonbigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigramsfiltered <- bigramsseparated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigramcounts <- bigramsfiltered %>% 
  count(word1, word2, sort = TRUE)


# bigram as tf-idf
bigramsunited <- bigramsfiltered %>%
  unite(bigram, word1, word2, sep = " ")

bigramtfidf <- bigramsunited %>%
  count(date, bigram) %>%
  bind_tf_idf(bigram, date, n) %>%
  arrange(desc(tf_idf))

#bigramtfidf

# Visualizing bigrams
library(igraph)
#bigramcounts

bigramgraph <- bigramcounts %>%
  filter(n > 2) %>%
  graph_from_data_frame()

set.seed(2017) 

ggraph(bigramgraph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


set.seed(2017)
```

#Bigrams for year 2018
```{r}
elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))

elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only

elon <- elon%>%
  filter(date == 2018)

elonbigrams <- elon %>%
  unnest_tokens(bigram, tweet, token = "ngrams", n = 2)

elonbigrams %>%
  count(bigram, sort = TRUE)

# bigrams with stop words
bigramsseparated <- elonbigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigramsfiltered <- bigramsseparated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigramcounts <- bigramsfiltered %>% 
  count(word1, word2, sort = TRUE)


# bigram as tf-idf
bigramsunited <- bigramsfiltered %>%
  unite(bigram, word1, word2, sep = " ")

bigramtfidf <- bigramsunited %>%
  count(date, bigram) %>%
  bind_tf_idf(bigram, date, n) %>%
  arrange(desc(tf_idf))

#bigramtfidf

# Visualizing bigrams
library(igraph)
#bigramcounts

bigramgraph <- bigramcounts %>%
  filter(n > 5) %>%
  graph_from_data_frame()

set.seed(201) 

ggraph(bigramgraph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


set.seed(2018)
```

#Bigrams for year 2019
```{r}
elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))

elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only
elon <- elon%>%
  filter(date == 2019)

elonbigrams <- elon %>%
  unnest_tokens(bigram, tweet, token = "ngrams", n = 2)

elonbigrams %>%
  count(bigram, sort = TRUE)

# bigrams with stop words
bigramsseparated <- elonbigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigramsfiltered <- bigramsseparated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigramcounts <- bigramsfiltered %>% 
  count(word1, word2, sort = TRUE)


# bigram as tf-idf
bigramsunited <- bigramsfiltered %>%
  unite(bigram, word1, word2, sep = " ")

bigramtfidf <- bigramsunited %>%
  count(date, bigram) %>%
  bind_tf_idf(bigram, date, n) %>%
  arrange(desc(tf_idf))

#bigramtfidf

# Visualizing bigrams
library(igraph)
#bigramcounts

bigramgraph <- bigramcounts %>%
  filter(n > 6) %>%
  graph_from_data_frame()

set.seed(2019) 

ggraph(bigramgraph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


set.seed(2019)
```
#Bigrams for year 2020
```{r}
elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))

elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only
elon <- elon%>%
  filter(date == 2020)

elonbigrams <- elon %>%
  unnest_tokens(bigram, tweet, token = "ngrams", n = 2)

elonbigrams %>%
  count(bigram, sort = TRUE)

# bigrams with stop words
bigramsseparated <- elonbigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigramsfiltered <- bigramsseparated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigramcounts <- bigramsfiltered %>% 
  count(word1, word2, sort = TRUE)


# bigram as tf-idf
bigramsunited <- bigramsfiltered %>%
  unite(bigram, word1, word2, sep = " ")

bigramtfidf <- bigramsunited %>%
  count(date, bigram) %>%
  bind_tf_idf(bigram, date, n) %>%
  arrange(desc(tf_idf))

#bigramtfidf

# Visualizing bigrams
library(igraph)
#bigramcounts

bigramgraph <- bigramcounts %>%
  filter(n > 6) %>%
  graph_from_data_frame()

set.seed(2017) 

ggraph(bigramgraph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


set.seed(2017)
```

#Bigrams for year 2021
```{r}
elon <- read.csv("2021.csv")
elon <- subset(elon, select=c(5,8))

elon$tweet <- gsub("[^\x01-\x7F]", "", elon$tweet)  #To remove emojis from tweets
elon$tweet = gsub("&amp", "", elon$tweet)           #To convert "&amp" to "&"
elon$tweet <- gsub("[[:punct:]]", "", elon$tweet)   #To remove special characters from tweets
elon$date = format(as.Date(elon$date, format="%Y-%m-%d %H:%M:%S"),"%Y") #converting timestampto YEAR only

elon <- elon%>%
  filter(date == 2021)

elonbigrams <- elon %>%
  unnest_tokens(bigram, tweet, token = "ngrams", n = 2)

elonbigrams %>%
  count(bigram, sort = TRUE)

# bigrams with stop words
bigramsseparated <- elonbigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigramsfiltered <- bigramsseparated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigramcounts <- bigramsfiltered %>% 
  count(word1, word2, sort = TRUE)


# bigram as tf-idf
bigramsunited <- bigramsfiltered %>%
  unite(bigram, word1, word2, sep = " ")

bigramtfidf <- bigramsunited %>%
  count(date, bigram) %>%
  bind_tf_idf(bigram, date, n) %>%
  arrange(desc(tf_idf))

#bigramtfidf

# Visualizing bigrams
library(igraph)
#bigramcounts

bigramgraph <- bigramcounts %>%
  filter(n > 1) %>%
  graph_from_data_frame()

set.seed(2017) 

ggraph(bigramgraph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


set.seed(2017)
```

